Practical Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-04-04 paper/paper.Rnw
Fix whitespace issue after \lstinline

% Priority queues.
% TODO: Check for whitespace error @ beginning of line this paragraph.
Priority queues are an abstract data structure allowing insertion of items with a given priority
and removal of the lowest-priority item in logarithmic time. Search trees and Heaps (which are
flattened representations of complete trees such that each node's key is at least as large as
those of both children) are concrete data structures which are usually used to implement sequential
priority queues. However, both require fairly elaborate reorganization after \lstinline|DeleteMin|
and/or \lstinline|Insert| operations, which are especially challenging to achieve in a concurrent
environment.

>>>>

% Priority queues.

Priority queues are an abstract data structure allowing insertion of items with a given priority
and removal of the lowest-priority item in logarithmic time. Search trees and Heaps (which are
flattened representations of complete trees such that each node's key is at least as large as
those of both children) are concrete data structures which are usually used to implement sequential
priority queues. However, both require fairly elaborate reorganization after
{\lstset{breakatwhitespace=true} \lstinline|DeleteMin|}
and/or \lstinline|Insert| operations, which are especially challenging to achieve in a concurrent
environment.
